Quantitative quality of lipid-cholesterol interactions in atomistic resolution molecular dynamics simulations

### 2016-10-04 MANUSCRIPT/manuscript.tex
Add authors
Updating from the original NMRlipids repo (#3)
* Add figure based on results at https://github.com/NMRLipids/NmrLipidsCholXray/issues/4

* Add results by Tom Piggot from https://github.com/NMRLipids/NmrLipidsCholXray/issues/4

@@

@@

% If you have acknowledgments, this puts in the proper section head.
\begin{acknowledgments}
% Put your acknowledgments here.
\end{acknowledgments}
\newpage
% Create the reference section using BibTe
\bibliography{refs.bib}

>>>>

\author{Peter Heftberger}
%\email[]{samuli.ollila@aalto.fi}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
\affiliation{University of Graz}

@@

\author{Georg Pabst}
\affiliation{University of Graz}

@@

% If you have acknowledgments, this puts in the proper section head.
\begin{acknowledgments}
% Put your acknowledgments here.
\end{acknowledgments}
\newpage
\appendix
\begin{center}
{\bf SUPPLEMENTARY INFORMATION}
\end{center}
\section{CHARMM36 results from different simulation packages}
The results from CHARMM36 model for lipid bilayers from different 
simulation packages have been reported to give different results in
the literature \cite{piggot12,lee16}. The results are mainly
dependent on different Lennart-Jones cut--off settings, but
all the details are not quite understood. In this work we use
the results from Gromacs 5 with settings suggested to be optimal
by Gromacs webpage. We also compared the results from Gromacs 5 with
these settings to the results simulated with NAMD, OpenMM and literature
values. The comparison is shown in Fig. \ref{programsCOMP}
 \begin{figure}[]
  \centering
  \includegraphics[width=8cm]{../FIGS/OrderParametersPROGRAMS.eps}

  \caption{\label{programsCOMP}
    Results for CHARMM36 model \cite{klauda10} from different simulation packages.
    Discussion going on at {\it https://github.com/NMRLipids/NmrLipidsCholXray/issues/4}.
  }
\end{figure}

% Create the reference section using BibTe
\bibliography{refs.bib}
